---
title: "Linear Model"
author: "Brandy Tovar"
date: "December 4, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(tigerstats)
```

```{r}
avast=read.csv("avast.csv")
attach(avast)
```

##Introduction

This data was taken from tigerstats. The data set contains observation from job applicants on their sim score are strength, grip and rating. We write these models as: 1. SIMS = f(ARMS) 2. SIMS = f(GRIP) 3. SIMS = f(ARM,GRIP)  


##First model
```{r}
model1=lm(SIMS~ARM)
summary.lm(model1)
```

The summary states the SIMS equation and shows that if and when put on a scatterplot, it creates a striaght line through the points on the plot.  

```{r}
plot(ARM,SIMS)
abline(model1)
```

This scatterplot shows that the SIMS = -4.09 + 0.5 = ARM. This equation is a straight line through the points on the scatterplot.   


The prediction interval from model1 when ARM = 88, GRIP = 94 is:  
```{r}
newdata= data.frame(ARM=88,GRIP=94)
predict(model1,newdata,interval = "predict")
```

The first predicted value is (fit) and the other two values are the lower and upper prediction values.  


##Second model
```{r}
model2=lm(SIMS~GRIP)
summary.lm(model2)
```

The summary states the SIMS equation and shows that if and when put on a scatterplot, it creates a striaght line through the points on the plot.   

```{r}
plot(GRIP,SIMS)
abline(model2)
```

This scatterplot shows that the SIMS = -4.09 + 0.5 = GRIP. This equation is a straight line through the points on the scatterplot.     


The prediction interval from model1 when SIMS = 95, GRIP = 94 is:   
```{r}
newdata= data.frame(SIMS=95,GRIP=94)
predict(model2,newdata,interval = "predict")
```

The first predicted value is (fit) and the other two values are the lower and upper prediction values.  

##Third model

```{r}
model3=lm(SIMS~ARM+GRIP)
summary.lm(model3)
```

The summary states the SIMS equation and shows that if and when put on a scatterplot, it creates a striaght line through the points on the plot.  


```{r}
plot(SIMS~ARM+GRIP)
abline(model3)
```

This scatterplot shows that the SIMS = -4.09 + 0.5 = ARM+GRIP. This equation is a straight line through the points on the scatterplot.       


The prediction interval from model1 when SIMS = 95, ARM = 88, GRIP = 94 is:  
```{r}
newdata= data.frame(SIMS=95,GRIP=94,ARM=88)
predict(model3,newdata,interval = "predict")
```

The first predicted value is (fit) and the other two values are the lower and upper prediction values.  

```{r}
anova(model1,model3)
```

The P-Value is 0.000004994 < 0.05 so we reject the null hypothesis and conclude that there is a difference between the two models.  

Model3 is greater since it has a smaller RSS than model1.  

The null hypothesis is that there is no difference between model1 and model3.  

The alternative hypothesis is that there is a difference between the models.  

